\begin{center}
\textbf{Acknowledgements}  % Acknowledgements
\end{center}
{\small
%\begin{CJK}{UTF8}{cwku}  % For Chinese typing
I am so grateful for the helps from my colleagues, aadvisors, collaborators and friends. They gave me a lots of help when I was struggle in the research and technical issue. Their kindness helps me to come over the advantages and receive the degree.
\newline
When I doing this project, my advisor and my collaborator, Prof. Kingman Cheung and Prof Shih-Chieh Hsu gave me so much support that makes me can find a path to accomplish this project. Their suggestions and strong knowledge support are my best backup when I struggled in the mist.  My colleague, Yi-Lun Chung, who helps me to resolve the problem of simulation package and theoretical problems, is also a person who deserved my most gratitude. 
\newline
I appreciate all the collaborator who participate in this project, Mike Fenton,  Alexander Shmakov, Daniel Whiteson, and Pierre Baldi. I would not finsihed this project without their help and support. The way that Alexander construct a machine learning model and the way that Mike describing a physics concept really teach me a lot. The guidence of Daniel, Shih-Chieh, and Pierre inspire me to explore more.

我想感謝我的同事、教授、朋友以及合作者。若沒有他們的鼎力相助，我肯定無法順利地完成這個研究。在我遇到各種問題，在困難中掙扎時，他們友善的協助讓我跨越難關，最後終於取得了學位。

張敬民教授以及徐士傑教授作為我的指導教授以及合作者，不論在物理上或是機器學習上，都非常大方地給予我非常多的建議。這些建議讓我能夠以足夠的知識來執行這個研究。他們的建議，每每都在我遇到困難時發揮關鍵的作用，也在我陷入迷霧時給予了我一盞明燈。

鍾沂倫，研究室的博士班學長，也在研究中給予了我相當大的幫助。無論是在各種環境的設定以及工作站的維護，乃至模擬軟體的設定以及物理模型的參數設定，都給了我非常多的幫助。他的協助讓我在維護工作站以及管理上輕鬆了非常多，真的是非常感謝他的幫忙。
\newpage